\section{Conclusion}

We presented \DynaSCSH, a dynamic framework for maintaining size-constrained $(k,\mathcal{P})$-truss communities over evolving heterogeneous information networks under projected source-edge updates. \DynaSCSH combines three technical contributions: (1) a count-based $O(|E|)$ Meta-Path Triangle Index with $O(d_{\mathcal{P}}^2)$ projected-edge updates, (2) an internal support cache that makes validation independent of the full graph size, and (3) a localized repair mechanism that preserves the original query node and validates internal support plus triangle connectivity before returning a repaired community.

Evaluation across 22 fixed-query synthetic DBLP configurations and a 26,850-node hybrid Planted Community Benchmark demonstrates incremental maintenance under a fixed-query baseline. Insertions preserve identity exactly: Jaccard is 1.000 in all insertion runs, average \qratio is 1.000, and average speedup is 3,824$\times$. Deletions show natural divergence (Jaccard 0.36--0.54, \qratio 0.89--0.92), and the D1 deletion stress run exposes the fallback-dominated lower bound (1.4$\times$ speedup) under strict invariant checking. The hybrid benchmark confirms scalability (random updates $<$1\,ms on 128K edges), 5,900--10,700$\times$ speedup, and repair feasibility (10/30 targeted repairs at $k$=2).

\textbf{Limitations.} \DynaSCSH currently supports a single meta-path, assumes updates over the projected source-type graph, and requires the size bound $s$ to be specified a priori. Raw HIN relation updates require a projection-refresh layer or index rebuild. The fast-path hit rate depends on the community's internal edge count relative to the update distribution and should be measured per deployment. The current local repair heuristic handles one-node replacement with strict $h$-hop BFS candidate search; multi-node repair and stronger replacement ranking are natural next steps. Extending the framework to multiple meta-paths, automatically recommending $s$, and maintaining communities over temporal sliding windows remain open directions.
