% VLDB template using acmart
\documentclass[sigconf, nonacm]{acmart}
\usepackage{pvldb}

\usepackage{amsmath,amsfonts}
\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{graphicx}
\graphicspath{{figures/}}
\usepackage{textcomp}
\usepackage{xcolor}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{xspace}
\usepackage{tikz}
\usetikzlibrary{arrows.meta, positioning, fit, backgrounds, shapes.geometric}
\settopmatter{printacmref=false}

\newcommand{\DynaSCSH}{\textsc{DYNASCSH}\xspace}
\newcommand{\mtindex}{\textsc{MT-INDEX}\xspace}
\newcommand{\qratio}{\text{$Q$-Ratio}\xspace}

%% PVLDB metadata. Replace DOI/pages after acceptance.
\renewcommand\vldbdoi{XX.XX/XXX.XX}
\renewcommand\vldbpages{XXX-XXX}
\renewcommand\vldbvolume{20}
\renewcommand\vldbissue{1}
\renewcommand\vldbyear{2027}
\renewcommand\vldbtitle{Dynamic Size-Constrained Community Search over Evolving Heterogeneous Information Networks}
\renewcommand\vldbavailabilityurl{https://github.com/wzw7234895/DynaSCSH}

\begin{document}

\title[Dynamic Size-Constrained Community Search]{Dynamic Size-Constrained Community Search over\texorpdfstring{\\}{ }Evolving Heterogeneous Information Networks}

\author{Zhiwei Wang}
\affiliation{%
  \institution{Dalian Maritime University}
  \city{Dalian}
  \country{China}
}
\email{wzw7234895@gmail.com}

\begin{abstract}
Heterogeneous information networks (HINs) model typed entities and relations. Community search on HINs identifies cohesive subgraphs containing a query node, with applications in recommendation, fraud detection, and expert finding. While Zhang et al. recently formalized the size-constrained variant and proved it NP-hard, their solution is inherently static---recomputing communities from scratch whenever the graph changes. Real-world HINs are dynamic: new collaborations form, products are purchased, and relationships evolve continuously.

We propose \DynaSCSH, a dynamic framework for maintaining size-constrained $(k,\mathcal{P})$-truss communities under projected source-edge insertions and deletions. \DynaSCSH combines three components: (1) a Meta-Path Triangle Index (\mtindex) storing $O(|E|)$ integer support counts and updating all co-triangle edge supports affected by a source-edge change, (2) an internal support cache that makes community validation independent of the full graph size, and (3) a localized repair mechanism with bounded-hop candidate search that validates support, size, query containment, and triangle connectivity before returning a repaired community.

Experiments on 22 fixed-query synthetic DBLP configurations and a hybrid Planted Community Benchmark (26,850 nodes, 128,227 edges) demonstrate the properties of incremental maintenance. On insertion-only streams, \DynaSCSH preserves community identity exactly (Jaccard=1.000, avg.\ \qratio=1.000, avg.\ 3,824$\times$ speedup vs.\ static recompute). Deletion and mixed streams introduce natural divergence: deletion Jaccard spans 0.36--0.54 (\qratio=0.89--0.92), reflecting the inherent difficulty of maintaining a fixed-size community under edge removal. The hybrid benchmark confirms scalability to 128K-edge graphs (random updates $<$1\,ms, 5,900--10,700$\times$ speedup) and demonstrates localized repair success (10/30 targeted community-edge deletions repaired at $k$=2). Strict invariant checking (support, size, query containment, triangle connectivity) makes fallback recomputation explicit when local repair cannot certify validity.
\end{abstract}

\maketitle

\vldbtopmatter

\input{sections/s1_introduction}
\input{sections/s2_related}
\input{sections/s3_preliminaries}
\input{sections/s4_method}
\input{sections/s5_experiments}
\input{sections/s6_conclusion}

\bibliographystyle{ACM-Reference-Format}
\bibliography{references}

\end{document}
